Donald Trump's Contributor Analysis by Yamin
========================================================
#Data Description
--------------------------------------------------------------- 

CMTE_ID			COMMITTEE ID				S
CAND_ID			CANDIDATE ID				S
CAND_NM			CANDIDATE NAME				S
CONTBR_NM		CONTRIBUTOR NAME			S
CONTBR_CITY		CONTRIBUTOR CITY			S
CONTBR_ST		CONTRIBUTOR STATE			S
CONTBR_ZIP		CONTRIBUTOR ZIP CODE			S
CONTBR_EMPLOYER		CONTRIBUTOR EMPLOYER			S
CONTBR_OCCUPATION	CONTRIBUTOR OCCUPATION			S
CONTB_RECEIPT_AMT	CONTRIBUTION RECEIPT AMOUNT		N
CONTB_RECEIPT_DT	CONTRIBUTION RECEIPT DATE		D	
RECEIPT_DESC		RECEIPT DESCRIPTION			S
MEMO_CD			MEMO CODE				S
MEMO_TEXT		MEMO TEXT				S
FORM_TP			FORM TYPE				S
FILE_NUM		FILE NUMBER				N
TRAN_ID			TRANSACTION ID				S
ELECTION_TP		ELECTION TYPE/PRIMARY GENERAL INDICATOR S


Data Type:  S = string (alpha or alpha-numeric); D = date; N = numeric  

--------------------------------------------------------------- 

## Variable Documentation 


COMMITTEE ID  
String   

A 9-character alpha-numeric code assigned to a committee by the Federal Election Commission. 

---------
CANDIDATE ID  
String   

A 9-character alpha-numeric code assigned to a candidate by the Federal Election Commission. 

---------
CANDIDATE NAME
String

---------
CONTRIBUTOR NAME
String

Reported name of the contributor.

---------
CONTRIBUTOR CITY
String

Reported city of the contributor.

---------
CONTRIBUTOR STATE
String

Reported state of the contributor.

---------
CONTRIBUTOR ZIP CODE
String

Reported zip code of the contributor.

---------
CONTRIBUTOR EMPLOYER
String

Reported employer of the contributor.

---------
CONTRIBUTOR OCCUPATION
String

Reported occupation of the contributor.

---------
CONTRIBUTION RECEIPT AMOUNT
Numeric

Reported contribution amount.

---------
CONTRIBUTION RECEIPT DATE
Date	

Reported contribution receipt date.  The date format is DD-MMM-YYYY.

---------
RECEIPT DESCRIPTION
String

Additional information reported by the committee about a specific contribution. 

---------
MEMO CODE
String

'X' indicates the reporting committee has provided additional text to describe a specific contribution.  See the MEMO TEXT.  

---------
MEMO TEXT
String

Additional information reported by the committee about a specific contribution.  

---------
FORM TYPE
Sting

Indicates what schedule and line number the reporting committee reported a specific transaction.   
SA17A:  Form 3P Schedule A Line 17A
SA18:   Form 3P Schedule A Line 18
SB28A:  Form 3P Schedule B Line 28A  

---------
FILE NUMBER
Numeric

A unique number assigned to a report and all its associated transactions.   
Use the file number to link transactions to the report summaries (Form 3P) in REPORT_SUMMARIES_FORM_3P.ZIP on the FEC's FTP server.  
ftp://ftp.fec.gov/FEC/Presidential_Map/

---------
TRANSACTION ID
String

A unique identifier permanently associated with each itemization or transaction appearing in an FEC electronic file.

---------
ELECTION TYPE / PRIMARY-GENERAL INDICATOR
String 

This code indicates the election for which the contribution was made. EYYYY (election plus election year)
P = Primary
G = General
O = Other
C = Convention
R = Runoff
S = Special
E = Recount
```{r echo=FALSE, message=FALSE, warning=FALSE, packages}
# Load all of the packages that you end up using
# in your analysis in this code chunk.

# Notice that the parameter "echo" was set to FALSE for this code chunk.
# This prevents the code from displaying in the knitted HTML output.
# You should set echo=FALSE for all code chunks in your file.

library(ggplot2)
library(dplyr)
```

```{r echo=FALSE, Load_the_Data}
# Load the Data
dt<-read.csv('/Users/apple/DAND/P4_DataAnalysis_with_R/P80001571-ALL.csv',header = T, row.names = NULL)
#fix the column names
c <- colnames(dt)
c <- c[2:length(c)]
colnames(dt) <- c
str(dt)
```
# Data wrangling 
## fix the data types
```{r}
#character to date
dt$contb_receipt_dt<-as.Date(dt$contb_receipt_dt,format='%d-%b-%y')
```
## clean the data
```{r}
#change negative receipt amount to positive
dt$contb_receipt_amt<-abs(dt$contb_receipt_amt)
```

# Univariate Plots Section
```{r}
#by contributor
dt.c<-dt%>%
  group_by(contbr_nm,contbr_zip,contbr_employer,contbr_occupation)%>%
  summarise(total_amount=sum(contb_receipt_amt),
            frequency=n())
```

## Time
```{r echo=FALSE, Univariate_Plots}
#outlier
dt.t<-dt[(format(dt$contb_receipt_dt,format = "%Y")=="2015"|format(dt$contb_receipt_dt,format = "%Y")=="2016"),]
ggplot(dt.t,aes(contb_receipt_dt))+
  geom_freqpoly()
```
## Frequency
```{r}
summary(dt.c$frequency)
```
从数据来看捐一次的最多,最高78次
```{r}
ggplot(data=dt.c,aes(frequency,fill=frequency))+
  geom_histogram(binwidth = 1)+
#transform the coord
  coord_trans(y='sqrt')+
  scale_x_continuous(breaks=seq(1,78),'times per contributor')+
  scale_fill_brewer(palette = 'Reds')
```
### Find the biggest fan
```{r}
subset(dt.c,frequency==max(frequency))
```
##Amount
```{r}

```

## Occupation
```{r}
#subset the data
dt.oc<-dt.c%>%
  group_by(contbr_occupation)%>%
  summarise(n=n())%>%
  arrange(desc(n))%>%
  mutate(percentage=n/sum(n))
dt.oc
```
find some dirty data.
### Clean the data
```{r}
#REGISTERED NURSE
dt$contbr_occupation[dt$contbr_occupation=='RN'|dt$contbr_occupation=='NURSE']<-'REGISTERED NURSE'
#SELF-EMPLOYED
dt$contbr_occupation[grepl('SELF',dt$contbr_occupation)]<-'SELF-EMPLOYED'
#BUSINESS OWNER
dt$contbr_occupation[grepl('OWNER',dt$contbr_occupation)]<-'BUSINESS OWNER'
#REALTOR
dt$contbr_occupation[grepl('REAL',dt$contbr_occupation)]<-'REALTOR'
#TEACHER
dt$contbr_occupation[grepl('TEACHER',dt$contbr_occupation)]<-'TEACHER'
#INSURANCE
dt$contbr_occupation[grepl('INSURANCE',dt$contbr_occupation)]<-'INSURANCE'
#SALES
dt$contbr_occupation[grepl('SALES',dt$contbr_occupation)]<-'SALES'
#FARMER/RANCHER
dt$contbr_occupation[grepl('FARM',dt$contbr_occupation)|grepl('RANCH',dt$contbr_occupation)]<-'FARMER/RANCHER'
#TRUCK DRIVER
dt$contbr_occupation[grepl('TRUCK',dt$contbr_occupation)]<-'TRUCK DRIVER'
#ACCOUNTANT
dt$contbr_occupation[grepl('ACCOUNT',dt$contbr_occupation)|grepl('CPA',dt$contbr_occupation)]<-'ACCOUNTANT'
#LAWYER
dt$contbr_occupation[grepl('ATTORNEY',dt$contbr_occupation)]<-'LAWYER'
#DENTIST
dt$contbr_occupation[grepl('DENTIST',dt$contbr_occupation)]<-'DENTIST'
#PHYSICIAN
dt$contbr_occupation[grepl('PHYSICIAN',dt$contbr_occupation)]<-'PHYSICIAN'
```
### Plotting
```{R}
#plot
ggplot(subset(dt.oc,n>500),aes(x=reorder(contbr_occupation,n), y=n,fill=contbr_occupation))+
  geom_col(width=1, color="white")+
  geom_text(aes(label=n), color="black",
                   hjust=1.0, size=3)+
  theme(legend.position="none")+
  coord_flip()+
#标签优化
  xlab('Occupation')+
  ylab('Number of People')
```
观察得，退休的最多，做小生意的其次。

# Bivariate Plots Section
```{r echo=FALSE, Bivariate_Plots}

```

# Bivariate Analysis

### Talk about some of the relationships you observed in this part of the investigation. How did the feature(s) of interest vary with other features in the dataset?

### Did you observe any interesting relationships between the other features (not the main feature(s) of interest)?

### What was the strongest relationship you found?




# Multivariate Plots Section

```{r echo=FALSE, Multivariate_Plots}

```

# Multivariate Analysis

### Talk about some of the relationships you observed in this part of the investigation. Were there features that strengthened each other in terms of looking at your feature(s) of interest?

### Were there any interesting or surprising interactions between features?

### OPTIONAL: Did you create any models with your dataset? Discuss the strengths and limitations of your model.

------

# Final Plots and Summary

### Plot One
```{r echo=FALSE, Plot_One}

```

### Description One


### Plot Two
```{r echo=FALSE, Plot_Two}

```

### Description Two


### Plot Three
```{r echo=FALSE, Plot_Three}

```

### Description Three

------

# Reflection
